Q1: Are lake and terrestrial primary productivity coherent?

### 2019-10-04 AnalysisCode/ms1_prep.Rmd
ms1 analysis updates
analyses updates in progress

```{r limno import and formatting, echo=TRUE, cache=TRUE}

@@

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "nhd_fcode", "hu4_zoneid", 
                                                           "hu12_zoneid", "state_zoneid", "elevation_m"), tsvars=c("chla"), 
                                  minmos=3, minobs=3, timespan=c(1989,2018))
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)

@@

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1.RData")

>>>>

```{r limno import and formatting, echo=TRUE, cache=FALSE}

@@

lagoslakes.raw<-makeLAGOSannualts(lakes_to_get, infovars=c("lake_area_ha", "lake_perim_meters", "nhd_ftype", "nhd_fcode", "hu4_zoneid", 
                                                           "hu12_zoneid", "state_zoneid", "elevation_m"), tsvars=c("chla"), 
                                  minmos=3, minobs=3, timespan=c(1989,2018),lagosversion="1.087.3")
lagoslakes.cln<-cleanAnnualts(lagoslakes.raw)

@@

save.image("/Users/jonathanwalter/Box Sync/NSF EAGER Synchrony/Data/RData files/ms1_analysis_inprogress1_v10873.RData")
